On $K_2$-analogue of Serre problem for $\SL_4$

### 2018-08-19 paper.tex
Minor

For $m\geq 2$ define $G_m$ as the group presented by generators $\mathcal{X}_m$ and the following three families of relations:
\begin{align}
 \label{eq:am} \tag{$a_m$} x_{\alpha}(\xi) x_{\alpha}(\eta) & = x_{\alpha}(\xi+\eta),&  \xi,\eta\in B_d,\ d\leq m;&\\
 \label{eq:bm} \tag{$b_m$} [x_\alpha(\xi), x_{\beta}(\eta))] &  = 1, & \text{in the case $\alpha+\beta\not\in\Phi\cup\{0\}$,}\\
 \nonumber                                                     &       & \xi \in B_d,\ \eta \in B_e,\ d,e\leq m;\\
 \label{eq:cm} \tag{$c_m$} [x_\alpha(\xi), x_{\beta}(\eta)] & = x_{\alpha+\beta}(N_{\alpha,\beta}\xi\eta), & \text{in the case $\alpha+\beta\in \Phi$,}\\
 \nonumber                                                    &  & \xi \in B_d,\ \eta \in B_e,\ d, e, d+e \leq m.
 \end{align}
For $m=1$ define $G_1$ as the group presented by generators $\mathcal{X}_m$, three families of relations $a_1, b_1, c_1$ as above and the following additional family of relations:
\begin{align}  \label{eq:d1} \tag{$d_1$} [[x_{\alpha}(\xi), x_{\beta+\gamma}(\eta)], x_{\beta}(\zeta) ] & = 1, 
 & \xi,\eta,\zeta\in B_1,\ \text{ $(\alpha, \beta, \gamma)$ is an $\rA_3$-triple }.
\end{align}
% (this can be replaced by the weaker assumption that $A$ is additively generated by its units).

It is clear that the natural embedding of generators $\mathcal{X}_n \subseteq \mathcal{X}_{n+1}$ induces
 a map $\theta_n\colon G_n \to G_{n+1}$.
Our main goal is to show the following result.
\begin{prop}\label{prop:tul3.3}
 For $n\geq 1$ the map $\theta_n$ is an isomorphism. Consequently, $\St(\Phi, B)$ can be presented by generators $\mathcal{X}_1$
  and families of relations $(a_1)$, $(b_1)$, $(c_1)$, $(d_1)$.
\end{prop}
%TODO: Deduce 2nd assertion from 1st
To prove~\cref{lem:tul3.3} it suffices to show that the natural map $\theta_m \colon G_m \to G_{m+1}$ is an isomorphism for $m\geq 2$.
Indeed, this would give the required isomorphism $G_1 \cong \St(\Phi, B)$ since $\langle \XX{\infty} \mid \RR{\infty} \rangle$ is evidently isomorphic to $\St(\Phi, B)$.
%Denote by $F(S)$ the free group on the generating set $S$.
%It is clear that $\RR{n}\subseteq\RR{n+1}$, moreover $\langle \RR{n} \rangle = \langle \RR{\infty}\rangle \cap F(\XX{n})$.
%well, not so clear, actually :)

@@

The following lemma is reminiscent of~\cite[Proposition 1.1]{Re75} and~\cite[Proposition~3.2.2]{RS76}.
\begin{lemma}
 Suppose $m \geq 1$.
 Let $\alpha, \beta, \alpha', \beta'$ be such that $\alpha + \beta = \alpha' + \beta'$.
 Assume, moreover, that $\xi \in B_k$, $\xi' \in B_{k'}$, $\eta \in B_l$, $\eta' \in B_{l'}$ are such that 
  $N_{\alpha, \beta} \xi \eta = N_{\alpha', \beta'}\xi' \eta'$ for some $k,k',l,l'\leq m$ satisfying $k+l=k'+l' = m+1$.
 Then in the group $G_m$ the following relations hold:
 \begin{align}
  \label{item:i} [x_\alpha(\xi), x_\beta(\eta)] &= [x_{\alpha'}(\xi'), x_{\beta'}(\eta')] & \\
  \label{item:ii} [[x_\gamma(\zeta), [x_\alpha(\xi), x_\beta(\eta)]] & = 1 & \text{in the case } \gamma\in\{\alpha, \beta, \alpha + \beta\},\\
  \nonumber                                     &                          & \text{$\zeta \in B_{k''}$, $k''\leq m$.}
 \end{align}
\end{lemma}
\begin{proof}
 Notice that $k+l = m+1$, $k, l\leq m$ imply $k,l>0$, hence $B_i= t^i \cdot A$ for $i=k,k',l,'l'$.
 Therefore, we can repeat the argument of~\cite[Proposition 1.1]{Re75} verbatim.
\end{proof}

\begin{lemma} For every $\rA_3$-triple $(\alpha, \beta, \gamma)$ in $\Phi$ the following relation holds in the group $G_1$:
\begin{align} 
 [[x_{\beta}(b t), x_{\alpha}(a t)],  x_{\gamma}(c)] & = [x_{\alpha+\beta}(a b t),  x_{\gamma}(c t)].
\end{align}
 \end{lemma}
\begin{proof}
 \begin{align*}
   [[x_{\beta}(b t), x_{\alpha}(a t)],  x_{\gamma}(c)] = [{}^{x_{\beta}(b t)}\!x_{\alpha}(at), [x_{\gamma}(c),x_{\beta}(b t)]] &  \text{ by~\eqref{eq:H1iii} and~$(b_1)$} \\ 
                                                       = {}^{x_{\beta}(b t)}[ x_{\alpha}(at), x_{\beta +\gamma}(bct) ] & \text{ by $(b_1)$ and $(c_1)$}\\
                                                       = [x_{\alpha}(at), x_{\beta +\gamma}(bct)] & \text{ by $(d_1)$. \qedhere}
 \end{align*}

@@

To prove that $\theta_m$ is an isomorphism we construct the missing generators of $G_{m+1}$ in $G_m$ and then show that they satisfy relations $a_{m+1}$, $b_{m+1}$ and $c_{m+1}$.

>>>>

For $m\geq 2$ define $G_m$ as the group presented by generators $\mathcal{X}_m$ and the following three families of relations:
\begin{align}
 \label{eq:am} \tag{$a_m$} x_{\alpha}(\xi) x_{\alpha}(\eta) & = x_{\alpha}(\xi+\eta),&  \xi,\eta\in B_d,\ d\leq m;&\\
 \label{eq:bm} \tag{$b_m$} [x_\alpha(\xi), x_{\beta}(\eta))] &  = 1, & \text{in the case $\alpha+\beta\not\in\Phi\cup\{0\}$,}\\
 \nonumber                                                     &       & \xi \in B_d,\ \eta \in B_e,\ d,e\leq m;\\
 \label{eq:cm} \tag{$c_m$} [x_\alpha(\xi), x_{\beta}(\eta)] & = x_{\alpha+\beta}(N_{\alpha,\beta}\xi\eta), & \text{in the case $\alpha+\beta\in \Phi$,}\\
 \nonumber                                                    &  & \xi \in B_d,\ \eta \in B_e,\ d, e, d+e \leq m.
 \end{align}
For $m=1$ define $G_1$ as the group presented by generators $\mathcal{X}_m$, three families of relations $(a_1), (b_1), (c_1)$ as above and the following additional family of relations:
\begin{align}  \label{eq:d1} \tag{$d_1$} [[x_{\alpha}(\xi), x_{\beta+\gamma}(\eta)], x_{\beta}(\zeta) ] & = 1, 
 & \xi,\eta,\zeta\in B_1,\ \text{ $(\alpha, \beta, \gamma)$ is an $\rA_3$-triple }.
\end{align}
% (this can be replaced by the weaker assumption that $A$ is additively generated by its units).

The natural embedding of generators $\mathcal{X}_n \subseteq \mathcal{X}_{n+1}$ induces a map $\theta_n\colon G_n \to G_{n+1}$.
Our goal is to show the following result.
\begin{prop}\label{prop:tul3.3}
 For $n\geq 1$ the map $\theta_n$ is an isomorphism. Consequently, $\St(\Phi, B)$ can be presented by generators $\mathcal{X}_1$
  and families of relations $(a_1)$, $(b_1)$, $(c_1)$, $(d_1)$.
\end{prop}
%TODO: Deduce 2nd assertion from 1st
Notice that the second assertion follows from the first one.
Indeed, this would give the required isomorphism $G_1 \cong \St(\Phi, B)$ since $\langle \XX{\infty} \mid \RR{\infty} \rangle$ is evidently isomorphic to $\St(\Phi, B)$.
%Denote by $F(S)$ the free group on the generating set $S$.
%It is clear that $\RR{n}\subseteq\RR{n+1}$, moreover $\langle \RR{n} \rangle = \langle \RR{\infty}\rangle \cap F(\XX{n})$.
%well, not so clear, actually :)

@@

The following lemma is similar to~\cite[Proposition 1.1]{Re75} and~\cite[Proposition~3.2.2]{RS76}.
\begin{lemma}
 Suppose $m \geq 1$.
 Let $\alpha, \beta, \alpha', \beta'$ be such that $\alpha + \beta = \alpha' + \beta'$.
 Assume, moreover, that $\xi \in B_k$, $\xi' \in B_{k'}$, $\eta \in B_l$, $\eta' \in B_{l'}$ are such that 
  $N_{\alpha, \beta} \xi \eta = N_{\alpha', \beta'}\xi' \eta'$ for some $k,k',l,l'\leq m$ satisfying $k+l=k'+l' = m+1$.
 Then in the group $G_m$ the following relations hold:
 \begin{align}
  \label{item:i} [x_\alpha(\xi), x_\beta(\eta)] &= [x_{\alpha'}(\xi'), x_{\beta'}(\eta')] & \\
  \label{item:ii} [[x_\gamma(\zeta), [x_\alpha(\xi), x_\beta(\eta)]] & = 1 & \text{in the case } \gamma\in\{\alpha, \beta, \alpha + \beta\},\\
  \nonumber                                     &                          & \text{$\zeta \in B_{k''}$, $k''\leq m$.}
 \end{align}
\end{lemma}
\begin{proof}
 Notice that $k+l = m+1$, $k, l\leq m$ imply $k,l>0$, hence $B_i= t^i \cdot A$ for $i=k,k',l,'l'$.
 Thus, the argument of~\cite[Proposition 1.1]{Re75} can be repeated verbatim.
\end{proof}

\begin{lemma} For every $\rA_3$-triple $(\alpha, \beta, \gamma)$ in $\Phi$ the following relation holds in $G_1$:
\begin{align} 
 [[x_{\beta}(b t), x_{\alpha}(a t)],  x_{\gamma}(c)] & = [x_{\alpha}(at), x_{\beta+\gamma}(N_{\beta, \gamma}b c t)].
\end{align}
 \end{lemma}
\begin{proof}
 \begin{align*}
   [[x_{\beta}(b t), x_{\alpha}(a t)],  x_{\gamma}(c)] = [{}^{x_{\beta}(b t)}\!x_{\alpha}(at), [x_{\gamma}(c),x_{\beta}(b t)]] &  \text{ by~\eqref{eq:H1iii} and~$(b_1)$} \\ 
                                                       = {}^{x_{\beta}(b t)}[ x_{\alpha}(at), x_{\beta +\gamma}(N_{\beta,\gamma}bct) ] & \text{ by $(b_1)$ and $(c_1)$}\\ 
                                                       %TODO:  Missing structure constants...
                                                       = [x_{\alpha}(at), x_{\beta +\gamma}(N_{\beta,\gamma}bct)] & \text{ by $(d_1)$. \qedhere}
 \end{align*}

@@

To construct a map splitting to $\theta_m$ we construct the missing generators of $G_{m+1}$ in $G_m$ 
 and then show that they satisfy relations $a_{m+1}$, $b_{m+1}$ and $c_{m+1}$.
